Stagnating State Funding for Higher Education and its Effect on Faculty Composition at US Universities

### 2023-05-31 text/sections/07-conclusion.tex
standardised plot axies.

Public universities have systematically substituted away from tenure-track and tenured professors, towards non-tenured lecturers, in the face of persistent declines in state funding for higher education.
The effects on incumbent professors in the state of Illinois are non-distinguishable from zero, while suggestive information shows falls in hiring, which together implies that the changes in faculty composition are driven by reduced hiring of new professors.
Each year, public universities are using more contingent lecturers to teach their students, while private universities continue to employ more tenure-track and tenured professors than their public counterparts, and each year the gap widens.

>>>>

Public universities have systematically substituted away from tenure-track and tenured professors, towards non-tenured lecturers, in the face of persistent declines in state funding for higher education.
The effects on incumbent professors in the state of Illinois are non-distinguishable from zero, while suggestive information shows falls in hiring, which together implies that the changes in faculty composition are driven by reduced hiring of new professors.
Public universities are using more contingent lecturers to teach their students, while private universities continue to employ more tenure-track and tenured professors than their public counterparts, and each year the gap widens.
